ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura Gati).}

### 2018-06-07 Latex/Draft_Summer2018/Summer2018.tex
Keeeeep writing

Regarding the empirical section, the idea is to identify supply (technological) shocks which are only specific to the ICT sector in a standard Structural VAR.\footnote{An interesting paper which are somehow related to our empirical part is \cite{jafari2012impact}. The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In a multivariate system where TFP and ICT investment are ordered respectively first and second, we look for a shock which does not affect TFP on impact but that maximize the impact effect on ICT investment.

>>>>

Regarding the empirical section, the idea is to identify supply (technological) shocks which are only specific to the ICT sector in a standard Structural VAR.\footnote{An interesting paper which are somehow related to our empirical part is \cite{jafari2012impact}. The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In order to have a reliable identification procedure our multivariate system needs to embody three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP). Importantly, ICTI is defined as the total expenditure in equipment and computer software meant to be used in production for more than an year. Thus, an increase in ICTI has to be though as an ICT capital deepening. Moreover RP is simply the ration between prices in the ICT sector over prices in the overall economy. As pointed out by

In other words, In order to identify a ICT supply shock, we expect it to be orthogonal to current TFP because the ICT sector accounts for a negligible part in the whole economy. In addition, ICT supply shocks should enhance the usage of this ICT goods and services

 we seek a shock which are ordered respectively first and second, we look for a shock which does not affect TFP on impact but that maximize the impact effect on ICT investment.
